### 2025-02-28 sports-cognitive-psychology.qmd
20250228 - updates

As depicted in the @fig-goForItPercentageByWinProbChange (which was adapted from a [figure by Ben Baldwin](https://www.nfl4th.com/articles/4th-down-research.html); archived at <https://perma.cc/S5D8-3NCU>), teams went for it on fourth down about twice as often in 2021 compared to 2017, when teams would increase their win probably by going for it.

>>>>

As depicted in the @fig-goForItPercentageByWinProbChange (which was adapted from a [figure by Ben Baldwin](https://www.nfl4th.com/articles/4th-down-research.html); archived at <https://perma.cc/S5D8-3NCU>), teams went for it on fourth down about twice as often in 2021 compared to 2017, when when their win probability was at least 20% (given the current situation at the start of the given play) and they would increase their win probably by going for it.
